Multi-task learning in Computer Vision

### 2020-05-30 5-Multitask.tex
Add some fixes to all the things.

\chapter{Multi-task learning}
Multi-task learning is a generalization of Transfer Learning to training a single model where the goal is to optimize for multiple objectives.
Training a multi-task model requires a set of distinct tasks to be posed as a multi-task learning problem.
It can have many benefits when applied correctly, such as making the models more general by regularization and reducing computational requirements.
On the other hand, if multi-task learning is applied to problems that don't train well in a multi-task setting, the resulting models can be significantly worse than the single-task counterparts.

\section{Definition}
Multi-task learning is quite similar to transfer learning.
However, the main difference lies in the fact that the goal is to generalize to solve and improve performance in all tasks using some shared representation.
In contrast, transfer learning aims to optimize a single new task, ignoring the performance on the original entirely.
Often the shared layers are initialized using some ImageNet model and transfer learning as the ImageNet backbone is an architectural feature shared in many models.

@@

To train the network, each task ${T_i}$ needs to have its loss function defined.
A commonly used way to get the total loss of the input is by using the weighted loss functions for all tasks, resulting in a formula \[L_{total} = \sum_i{w_i L_i}\] \noindent where ${L_i}$ is the loss function for task ${T_i}$ and ${w_i}$ is the weight that specifies the sensitivity of the task \citep{usingUncertaintyToWeighLosses}.
The sensitivity of the tasks is an essential parameter to get right as choosing a too high parameter for some task might lead to a solution that is optimal for only the most sensitive task, starving the others \citep{whichTasks}.

Once the loss function is specified, the actual training is quite similar to training a single-task model.
The one new thing to consider in a multi-task setting is the sampling ratio of the different tasks as some tasks can be easier to learn or contain significantly more or less data compared to other tasks.
Like in regular training, the models are trained one batch at a time.
In a multi-task setting, we have datasets for each of the tasks from which we can pick at a time.
Now, we can define an epoch e in the training process as the total number of batches from all tasks.
The epoch can be formalized as \[ e = \sum_i{ \dfrac{|X_i| \alpha_i}{B_i}}\] \noindent batches over $i$ tasks, where $|X_i|$ is the training set size, $B_i$ is the batch size, and $\alpha_i$ is the scaling factor for each task, telling how important the specific task is.
Iterating through all batches can be done in a round-robin fashion, by going through all batches of each data set at a time or randomly sampling the sets with probabilities respective to their magnitude and scaling factor.

@@

Besides just deciding the network branching, each task requires an independent head that outputs prediction for that task.
These task heads are similar to those used in transfer learning, where only a single task is solved using the ImageNet backbone.
Especially in a multi-task setting, these heads can be more than just a single linear layer calculating the softmax over all classes.
A single head can contain any combination of several linear layers, dropout layers, batch normalization layers, convolutional layers, or it could be a Recurrent Neural Network creating a caption for the image embedding, depending on the task at hand.
In Figure 3.1, we can see an example of the flexibility of the sharing as the model can use a completely shared backbone or a branching backbone, which has a unique head for each task, solving the person re-identification and classification tasks.

@@

In Figure 3.2, there are multiple ways of configuring a multi-task network in terms of what to share.
The results for the different configurations were quite varied.
However, even the worst multi-task Model A did better on every task when compared to the single-task models, and accuracy improvement from the single-task case to the best multi-task Model F was roughly 20\% \citep{healthyDrink}.
These results are quite validating for the presumed benefits of multi-task models.
Since these results show that it is possible to share the majority of the network parameters and, at the same time, increase the performance, even with the most greedy share-all model.
Though, at the same time, it shows that multiple compute-expensive experiments have to done to find the most optimal sharing structure for the backbone network.

The two original features of interest were sugar and alcohol level in the drinks, and the other features were added as auxiliary training features to improve the performance \citep{healthyDrink}.
This auxiliary training can also be done by, for example, using ImageNet to keep the original classifier accurate on ImageNet while training on the new data set like in \citep{biologicalMultitask}; this way, the model won't be able to overfit on the new data so easily.
In the drink classification experiment, the auxiliary tasks were picked in a way that they might help in finding the correct features to solve the actual tasks \citep{healthyDrink}.
Adding auxiliary tasks is an interesting way of forcing features into the model that the developer thinks could be useful for the model to find, in that sense, they are hand-crafted features that get augmented in the model.
In practice, this means that if we are training a model to predict the steering angle, we might want to add an auxiliary task that predicts the lane markers to make it easier to learn these features.

A similar multi-task model in \citep{visualPerson}, also partly visualized in Figure 3.1, solves 6 different tasks in a single model.
The tasks in that model are very different from one another, including person re-identification, pose estimation and image segmentation.
The interesting result in their search for related tasks is that while a pair of tasks don't work well together, they can work well when combined with other tasks.
For example, they found that just pairing the pose estimation head with other tasks significantly reduces its accuracy, but when all tasks use the single shared backbone, it does just as well as if trained in a single-task setting.
These results show that very different tasks can combine to a single model to provide a very significant reduction in model size while producing about as good or better accuracies.

>>>>

\chapter{Multi-task learning}
Multi-task learning is a generalization of Transfer Learning to training a single model where the goal is to optimize for multiple objectives. 
Training a multi-task model requires a set of distinct tasks to be posed as a multi-task learning problem.
It can have many benefits when applied correctly, such as making the models more general by regularization and reducing computational requirements.
On the other hand, if multi-task learning is applied to problems that don't train well in a multi-task setting, the resulting models can be significantly worse than the single-task counterparts.
Here we look at examples of multi-task learning in computer vision.
Especially recently, with the introduction of transformers like BERT \citep{bert}, multi-task learning and transfer learning have gained popularity within natural language processing, but to restrict our scope, we only consider how to apply multi-task learning in computer vision.

\section{Definition}
Multi-task learning is quite similar to transfer learning. 
However, the main difference lies in the fact that the goal is to generalize to solve and improve performance in all tasks using some shared representation. 
In contrast, transfer learning aims to optimize a single new task, ignoring the performance on the original task entirely. 
Often in multi-task learning, the shared layers are initialized using some ImageNet model and transfer learning as the ImageNet backbone is an architectural feature shared in many models.

@@

To train the network, each task ${T_i}$ needs to have its loss function defined.
A commonly used way to get the total loss of the input is by using the weighted loss functions for all tasks, resulting in a formula \[L_{total} = \sum_i{w_i L_i}\] \noindent, where ${L_i}$ is the loss function for task ${T_i}$ and ${w_i}$, is the weight that specifies the sensitivity of the task \citep{usingUncertaintyToWeighLosses}. 
The sensitivity multiplies the loss of the task.
Multiplying the loss has the effect of making the error on the task with higher sensitivity to have a larger impact on the adjustment of weights.
So the sensitivity should be used to either pick tasks that are important or to normalize the losses if they are very different.
There can be significant differences in the scale of the losses if different tasks use different loss functions.
The sensitivity of the tasks is an essential parameter to get right as choosing a too high parameter for some task might lead to a solution that is optimal for only the most sensitive task, starving the others \citep{whichTasks}.

Once the loss function is specified, the actual training is quite similar to training a single-task model.
The one new thing to consider in a multi-task setting is the sampling ratio of the different tasks as some tasks can be easier to learn or contain significantly more or less data compared to other tasks.
Like in regular training, the models are trained one batch at a time. 
In a multi-task setting, we have datasets for each of the tasks from which we can pick at a time.
Now, we can define an epoch e in the training process as the total number of batches from all tasks. 
The epoch can be formalized as \[ e = \sum_i{ \dfrac{|X_i| \alpha_i}{B_i}}\] \noindent batches over $i$ tasks, where $|X_i|$ is the training set size, $B_i$ is the batch size, and $\alpha_i$ is the scaling factor for each task, telling how important the specific task is for the learning process.
The sampling ratio is one of the new parameters that is required when doing multi-task learning on multiple datasets.
When training models, some value has to be picked for the sampling ratios, and picking wrong values leads to worse models.
Precisely what is a good sampling ratio is complicated to tell beforehand, and generally, the chosen values need to be evaluated by experimentation.
Iterating through all batches can be done in a round-robin fashion, by going through all batches of each data set at a time or randomly sampling the sets with probabilities respective to their magnitude and scaling factor.

@@

Besides just deciding the network branching, each task requires an independent head that outputs prediction for that task.
These task heads are similar to those used in transfer learning, where only a single task is solved using the ImageNet backbone.
Especially in a multi-task setting, these heads can be more than just a single linear layer calculating the softmax over all classes.
A single head can contain any combination of several linear layers, dropout layers, batch normalization layers, convolutional layers, or it could be a Recurrent Neural Network creating a caption for the image embedding, depending on the task at hand.
In Figure 4.1, we can see an example of the flexibility of the sharing as the model can use a completely shared backbone or a branching backbone, which has a unique head for each task, solving the person re-identification and classification tasks.

@@

In Figure 4.2, there are multiple ways of configuring a multi-task network in terms of what to share.
The results for the different configurations were quite varied. 
However, even the worst multi-task Model A did better on every task when compared to the single-task models, and accuracy improvement from the single-task case to the best multi-task Model F was roughly 20\% \citep{healthyDrink}.
These results are quite validating for the presumed benefits of multi-task models.
Since these results show that it is possible to share the majority of the network parameters and, at the same time, increase the performance, even with the most greedy share-all model.
Though, at the same time, it shows that multiple compute-expensive experiments have to done to find the most optimal sharing structure for the backbone network.

In the experiments done by \citep{healthyDrink}, they utilized auxiliary training to great effect.
They had two original features of interest that were sugar and alcohol level in the drinks.
Other features were added as auxiliary training features to improve the performance on the two original features \citep{healthyDrink}.
This auxiliary training can also be done by, for example, using ImageNet to keep the original classifier accurate on ImageNet while training on the new data set like in \citep{biologicalMultitask}; this way, the model won't be able to overfit on the new data so easily.
In the drink classification experiment, the auxiliary tasks were picked in a way that they might help in finding the correct features to solve the actual tasks \citep{healthyDrink}.
Adding auxiliary tasks is an interesting way of forcing features into the model that the developer thinks could be useful for the model to find, in that sense, they are hand-crafted features that get augmented in the model.
In practice, this means that if we are training a model e.g., to predict the steering angle given an image, we might want to add an auxiliary task that predicts the lane markers to make it easier to learn these features as they should be a significant feature for producing correct outputs.

A similar multi-task model in \citep{visualPerson}, also partly visualized in Figure 3.1, solves 6 different tasks in a single model.
The tasks in that model are very different from one another, including person re-identification, pose estimation, and image segmentation.
The interesting result in their search for related tasks is that while a pair of tasks don't work well together, they can work well when combined with other tasks.
For example, they found that just pairing the pose estimation head with other tasks significantly reduces its accuracy, but when all tasks use the single shared backbone, it does just as well as if trained in a single-task setting.
These results show that very different tasks can combine to a single model to provide a very significant reduction in model size while producing about as good or better accuracies.

### 2020-05-30 7-Experiments.tex
Add some fixes to all the things.

\section{Mixed precision training}

@@

To further extend the generalizability, we will try to add a third somewhat similar classification task using the TensorFlow flowers dataset \citep{tfflowers}, which contains five different types of flowers. 
The assumption here would be that flowers could require similar features as the previous leaf classification tasks, thus when increasing the training data with a closely related task, we could increase the generalizability even further.

@@

\begin{figure}[h!] 
\centering 
\includegraphics[width=0.8\textwidth]{imgs/object_classification_architecture.png}
\caption{The architectures of the 14 head multi-task model and a single-task model. TODO: ADD IMAGE}
\end{figure}

@@

\begin{table}[]
    \centering
    \begin{tabular}{lccl}
        \multicolumn{1}{l}{\textbf{}}    & \multicolumn{1}{l}{\textbf{Multi-task}} & \multicolumn{1}{l}{\textbf{Single-task}} \\ \cline{2-3}
        \multicolumn{1}{l}{People} & \multicolumn{1}{c}{94\%}            & \multicolumn{1}{c}{-}                           \\ \hline
        \multicolumn{1}{l}{Man} & \multicolumn{1}{c}{-}               & \multicolumn{1}{c}{84\%}                        \\ \hline
        \multicolumn{1}{l}{Woman} & \multicolumn{1}{c}{-}               & \multicolumn{1}{c}{-}                           \\ \hline
        \multicolumn{1}{l}{Baby}       & \multicolumn{1}{c}{96\%}            & \multicolumn{1}{c}{-}                           \\ \hline
        \multicolumn{1}{l}{Sea}       & \multicolumn{1}{c}{-}               & \multicolumn{1}{c}{86\%}                        \\ \hline
        \multicolumn{1}{l}{River}       & \multicolumn{1}{c}{-}               & \multicolumn{1}{c}{-}                           \\ \hline
        \multicolumn{1}{l}{EfficientNet} & \multicolumn{1}{c}{94\%}            & \multicolumn{1}{c}{88\%}                        \\ \hline
        \multicolumn{1}{l}{ResNet}       & \multicolumn{1}{c}{96\%}            & \multicolumn{1}{c}{89\%}                        \\ \hline
        \multicolumn{1}{l}{ResNet}       & \multicolumn{1}{c}{96\%}            & \multicolumn{1}{c}{91\%}                        \\ \hline
        \multicolumn{1}{l}{ResNet}       & \multicolumn{1}{c}{96\%}            & \multicolumn{1}{c}{-}                           \\ \hline
        \multicolumn{1}{l}{EfficientNet} & \multicolumn{1}{c}{94\%}            & \multicolumn{1}{c}{88\%}                        \\ \hline
        \multicolumn{1}{l}{ResNet}       & \multicolumn{1}{c}{96\%}            & \multicolumn{1}{c}{89\%}                        \\ \hline
        \multicolumn{1}{l}{ResNet}       & \multicolumn{1}{c}{96\%}            & \multicolumn{1}{c}{91\%}                        \\ \hline
        \multicolumn{1}{l}{ResNet}       & \multicolumn{1}{c}{96\%}            & \multicolumn{1}{c}{-}                           \\ \hline
        \multicolumn{1}{l}{Average}       & \multicolumn{1}{c}{-}               & \multicolumn{1}{c}{85\%}                        \\ \hline
    \end{tabular}
    \caption{Accuracies on the data sets for both single-task and multi-task models.}
\end{table}

@@

To train the multi-task model, we experimented on various sampling ratios to find the best model.
Manually giving a meaningful sampling ratio is quite difficult due to the relatively large number of tasks in this multi-task model.
The various sampling ratios we tested for this data were equal sampling, data proportional sampling, and finally, some manual adjustments to the proportional sampling based on the results.
The proportional sampling was the one that produced the final best model.
It is quite an interesting result, considering just how small some of the classes are relative to the entire data set.
We tried adjusting the proportional ratios based on the difference from the single-task accuracies but could not find ratios that would have improved the performance.
Based on the previous results, we could say that there likely exists some ratios that could provide superior results, but finding them is too expensive.
With the best model, which was chosen based on the average accuracy on the validation data, the model achieved an average of 89\% accuracy in labeling all the tasks.
By average, we mean taking the accuracy of each task separately and averaging those averages and not the total ratio of correct classifications.

@@

\begin{figure}[h!] 
\centering 
\includegraphics[width=0.8\textwidth]{imgs/object_classification_architecture.png}
\caption{EfficientDet models for solving the object detection problem. In a) we have the basic object detector. In b) we have the recursive object detector. In c) we show the hypotetical multi-task model. TODO: ADD IMAGE}
\end{figure}

The second way of approaching this problem is to first train a model on the COCO classes and to create a detector for the cat and dog classes.
Using the high-level model, we can automatically create acceptable object detection labels for the 37 classes in the pets dataset.
Then we can initialize a 37 class object detector using the weights of the two-class model.
By having such a well-initialized model for the detection, the second part of the training focuses on learning the features to differentiate between the very similar classes.
An interesting question here is just how well the object detector works when the classes are so similar.
In an image classifier setting, it would make sense that the model could learn the subtle features that are unique to each of the classes.
As we previously covered, the object detector is a multi-task problem. 
It follows that the network has to both decide the anchors most likely containing an object and also determining the class of the object.
If we look at the classes for the COCO dataset for object detection, for example, we can see that there are 80 classes, but they are relatively difficult to mix up due to being quite distinct from one another. 
In Figure 6.3, we have an example of two images from the pets dataset showing two classes that would be relatively easy to mix up.

@@

The recursive multi-task model reached again slightly lower accuracies than the single task counterparts.
The AP score on the cat or dog detection task dropped by 0.02 and the accuracy on the pets classification dropped by 4\% to 89\%.
Interestingly, the detector task had a higher accuracy than the classification head had on the pets test set.
The better accuracy could result from the fact that classifying a cropped animal is easier than to classify it within a larger frame.
And since the object detector is relatively decent at finding the cat or dog candidates as a combination, these achieve better results.

Based on the numbers, we could say that the two-stage detector seems to be the better one.
The main downside to doing the two-stage detection is the fact that it would have to work one frame behind the video.
Since on the first loop, we would detect our objects in the first frame.
On the second frame we would pass the second frame and the cropped images that we found in the first frame.
If the classification is done in this manner, the inference time cost won't be that much as it will be just the head to get the classification outputs.
In the case that multiple videos would be run in parallel, this could possibly not be possible as at some point, the input could be too large to handle as a single batch.
On the other hand, the pure detector doesn't need such considerations.
The pure detector's problem is that it has some obvious downsides due to the artificial training set that was created for it.
Whereas the recursive model does relatively as well on all kinds of data, the pure detector seems to have issues when there are multiple objects to detect, or the size varies.
These issues likely stem from the fact that the pets dataset consists mostly of single relatively large animals, which is not always the case.
Because the training and test sets are from the same source, they are relatively similar, so the performance is very transferable between those tasks.
Some of the previously mentioned ways of training could alleviate this problem.
Perhaps by having two classifier heads and doing auxiliary training on the COCO cats and dogs could make the detector detect the animals better, and hopefully, the classifier could solve the problem for all sizes from the single source.
This modification is also pictured in Figure 6.4.

>>>>

@@

To further extend the generalizability, we will try to add a third somewhat similar classification task using the Oxford flowers102 dataset \citep{flowers102}, which contains 102 different types of flowers for classification. 
The assumption here would be that flowers could require similar features as the previous leaf classification tasks, thus when increasing the training data with a closely related task, we could increase the generalizability even further.

@@

\begin{figure}[h!] 
\centering 
\includegraphics[width=0.8\textwidth]{imgs/image-labeling.png}
\caption{Architectures for both single-and multi-task models. The model (a) is the single-task model, which is the same for all 14 tasks. Model (b) is the Multi-task model, which contains 14 heads for each of the classification tasks. For these classifiers we took both max and average pool to create the embedding.}
\end{figure}

@@

\begin{table}[]
    \centering
    \begin{tabular}{lccl}
        \multicolumn{1}{l}{\textbf{}}    & \multicolumn{1}{l}{\textbf{Multi-task}} & \multicolumn{1}{l}{\textbf{Single-task}} \\ \cline{2-3}
        \multicolumn{1}{l}{People} & \multicolumn{1}{c}{90\%}            & \multicolumn{1}{c}{89\%}                           \\ \hline
        \multicolumn{1}{l}{Man} & \multicolumn{1}{c}{87\%}               & \multicolumn{1}{c}{84\%}                        \\ \hline
        \multicolumn{1}{l}{Woman} & \multicolumn{1}{c}{86\%}               & \multicolumn{1}{c}{87\%}                           \\ \hline
        \multicolumn{1}{l}{Baby}       & \multicolumn{1}{c}{87\%}            & \multicolumn{1}{c}{93\%}                           \\ \hline
        \multicolumn{1}{l}{Sea}       & \multicolumn{1}{c}{89\%}               & \multicolumn{1}{c}{96\%}                        \\ \hline
        \multicolumn{1}{l}{River}       & \multicolumn{1}{c}{89\%}               & \multicolumn{1}{c}{88\%}                           \\ \hline
        \multicolumn{1}{l}{Bird} & \multicolumn{1}{c}{88\%}            & \multicolumn{1}{c}{89\%}                        \\ \hline
        \multicolumn{1}{l}{Car}       & \multicolumn{1}{c}{85\%}            & \multicolumn{1}{c}{94\%}                        \\ \hline
        \multicolumn{1}{l}{Clouds}       & \multicolumn{1}{c}{93\%}            & \multicolumn{1}{c}{93\%}                        \\ \hline
        \multicolumn{1}{l}{Dog}       & \multicolumn{1}{c}{87\%}            & \multicolumn{1}{c}{93\%}                           \\ \hline
        \multicolumn{1}{l}{Flower} & \multicolumn{1}{c}{85\%}            & \multicolumn{1}{c}{93\%}                        \\ \hline
        \multicolumn{1}{l}{Night}       & \multicolumn{1}{c}{87\%}            & \multicolumn{1}{c}{92\%}                        \\ \hline
        \multicolumn{1}{l}{Portrait}       & \multicolumn{1}{c}{89\%}            & \multicolumn{1}{c}{91\%}                        \\ \hline
        \multicolumn{1}{l}{Tree}       & \multicolumn{1}{c}{87\%}            & \multicolumn{1}{c}{92\%}                           \\ \hline
        \multicolumn{1}{l}{Average}       & \multicolumn{1}{c}{88\%}               & \multicolumn{1}{c}{91\%}                        \\ \hline
    \end{tabular}
    \caption{Accuracies on the data sets for both single-task and multi-task models.}
\end{table}

@@

To train the multi-task model, we experimented on various sampling ratios to find the best model.
Manually giving a meaningful sampling ratio is quite difficult due to the relatively large number of tasks in this multi-task model.
The various sampling ratios we tested for this data were equal sampling, data proportional sampling, and finally, some manual adjustments to the proportional sampling based on the results.
The proportional sampling was the one that produced the final best model.
It is quite an interesting result, considering just how small some of the classes are relative to the entire data set.
We tried adjusting the proportional ratios based on the difference from the single-task accuracies but could not find ratios that would have improved the performance.
Based on the previous results, we could say that there likely exists some ratios that could provide superior results, but finding them is too expensive.
With the best model, which was chosen based on the average accuracy on the validation data, the model achieved an average of 88\% accuracy in labeling all the tasks.
By average, we mean taking the accuracy of each task separately and averaging those averages and not the total ratio of correct classifications.

@@

\begin{figure}[h!] 
\centering 
\includegraphics[width=0.8\textwidth]{imgs/object_detect_combine.png}
\includegraphics[width=0.8\textwidth]{imgs/recursive.png}
\caption{EfficientDet models for solving the object detection problem. In a), we have the basic object detector. We show how we train on the COCO data first and then transfer the weights to the model for the pets data with predicted bounding boxes. In red the additions needed to train on both the original data and artificially labeled are shown. Both tasks could share the weights for the detector but would need to have their own class head.  In b), we have the recursive object detector. In yellow, we describe the path to train on the pets data. With green, we describe the path to train the cat or dog object detector. In blue, we show the first cycle of a new prediction. With purple, we show the second cycle for the new detection.}
\end{figure}

The second way of approaching this problem is to first train a model on the COCO classes and to create a detector for the cat and dog classes.
Using the high-level model, we can automatically create acceptable object detection labels for the 37 classes in the pets dataset.
Then we can initialize a 37 class object detector using the weights of the two-class model.
By having such a well-initialized model for the detection, the second part of the training focuses on learning the features to differentiate between the very similar classes.
An interesting question here is just how well the object detector works when the classes are so similar.
In an image classifier setting, it would make sense that the model could learn the subtle features that are unique to each of the classes.
As we previously covered, the object detector is a multi-task problem. 
It follows that the network has to both decide the anchors most likely containing an object and also determining the class of the object.
If we look at the classes for the COCO dataset for object detection, for example, we can see that there are 80 classes, but they are relatively difficult to mix up due to being quite distinct from one another. 
In Figure 6.5, we have an example of two images from the pets dataset showing two classes that would be relatively easy to mix up.

@@

The recursive multi-task model reached again slightly lower accuracies than the single task counterparts.
The AP score on the cat or dog detection task dropped by 0.02, and the accuracy on the pets classification dropped by 4\% to 89\%.
Interestingly, the detector task had a higher accuracy than the classification head had on the pets test set.
The better accuracy could result from the fact that classifying a cropped animal is easier than to classify it within a larger frame.
And since the object detector is relatively decent at finding the cat or dog candidates as a combination, these achieve better results.

Based on the numbers, we could say that the two-stage detector seems to be the better one.
The main downside to doing the two-stage detection is the fact that it would have to work one frame behind the video.
Since on the first loop, we would detect our objects in the first frame.
On the second frame, we would pass the second frame and the cropped images that we found in the first frame.
If the classification is done in this manner, the inference time cost won't be that much as it will be just the head to get the classification outputs.
In the case that multiple videos would be run in parallel, this could possibly not be possible as at some point, the input could be too large to handle as a single batch.
On the other hand, the pure detector doesn't need such considerations.
The pure detector's problem is that it has some obvious downsides due to the artificial training set that was created for it.
Whereas the recursive model does relatively as well on all kinds of data, the pure detector seems to have issues when there are multiple objects to detect, or the size varies.
These issues likely stem from the fact that the pets dataset consists mostly of single relatively large animals, which is not always the case.
Because the training and test sets are from the same source, they are relatively similar, so the performance is very transferable between those tasks.
Some of the previously mentioned ways of training could alleviate this problem.
Perhaps by having two classifier heads and doing auxiliary training on the COCO cats and dogs could make the detector detect the animals better, and hopefully, the classifier could solve the problem for all sizes from the single source.
This modification is also pictured in Figure 6.4.

### 2020-05-30 HY-CS-main.tex
Add some fixes to all the things.

% Set supervisors and examiners, use the titles according to the thesis language
% Prof. 
% Dr. or in Finnish toht. or tri or FT, TkT, Ph.D. or in Swedish... 
\supervisors{Prof. Laura Ruotsalainen}
\examiners{Prof. Laura Ruotsalainen, Dr.~O.~Why}

@@

%% OPTIONAL STEP: Set up properties and metadata for the pdf file that pdfLaTeX makes.
%% Your name, work title, and keywords are recommended.
\hypersetup{
    unicode=true,           % to show non-Latin characters in Acrobat’s bookmarks
    pdftoolbar=true,        % show Acrobat’s toolbar?
    pdfmenubar=true,        % show Acrobat’s menu?
    pdffitwindow=false,     % window fit to page when opened
    pdfstartview={FitH},    % fits the width of the page to the window
    pdftitle={},            % title
    pdfauthor={},           % author
    pdfsubject={},          % subject of the document
    pdfcreator={},          % creator of the document
    pdfproducer={pdfLaTeX}, % producer of the document
    pdfkeywords={something} {something else}, % list of keywords for
    pdfnewwindow=true,      % links in new window
    colorlinks=true,        % false: boxed links; true: colored links
    linkcolor=black,        % color of internal links
    citecolor=black,        % color of links to bibliography
    filecolor=magenta,      % color of file links
    urlcolor=cyan           % color of external links
}

>>>>

% Set supervisors and examiners, use the titles according to the thesis language
% Prof. 
% Dr. or in Finnish toht. or tri or FT, TkT, Ph.D. or in Swedish... 
\supervisors{Associate Professor Laura Ruotsalainen}
\examiners{Associate Professor Laura Ruotsalainen, Professor Jyrki Kivinen }

@@

%% OPTIONAL STEP: Set up properties and metadata for the pdf file that pdfLaTeX makes.
%% Your name, work title, and keywords are recommended.
\hypersetup{
    unicode=true,           % to show non-Latin characters in Acrobat’s bookmarks
    pdftoolbar=true,        % show Acrobat’s toolbar?
    pdfmenubar=true,        % show Acrobat’s menu?
    pdffitwindow=false,     % window fit to page when opened
    pdfstartview={FitH},    % fits the width of the page to the window
    pdftitle={Multi-task learning in Computer Vision},            % title
    pdfauthor={Konsta Kutvonen},           % author
    pdfsubject={},          % subject of the document
    pdfcreator={},          % creator of the document
    pdfproducer={pdfLaTeX}, % producer of the document
    pdfkeywords={something} {something else}, % list of keywords for
    pdfnewwindow=true,      % links in new window
    colorlinks=true,        % false: boxed links; true: colored links
    linkcolor=black,        % color of internal links
    citecolor=black,        % color of links to bibliography
    filecolor=magenta,      % color of file links
    urlcolor=cyan           % color of external links
}
